\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-07-02 exps.tex
need to make \centering work for table

% As one can see in Table \ref{table:benchmark}, BCRT and WCRT of overall
% programs are smaller when they run on TP-JOP. For example, WCRT and BCRT
% of HRTCS are \(\times\)11.9 and \(\times\)3.4 smaller, respectively, for
% TP-JOP (0.0028, 0.0329 ms) compared to JOP (0.0334, 0.1120 ms). On the
% other hand, required logical delays \emph{d} are generally bigger on
% TP-JOP e.g. \(\times\)4.5 - \(\times\)5.9 and \(\times\)30.9 in Motor
% and Robot respectively. It is expected as their BCRT and WCRT
% differences are bigger on TP-JOP.  This also led to greater increase in
% minimum upper real-time bounds \emph{N} for TP-JOP in every example.  In
% AECS, there are two clock-domains using delay constructs that each has
% their own BCRT and WCRT. Again, individual BCRT and WCRT is smaller
% whereas \emph{d} is bigger on TP-JOP. One important property to note
% here, is that BCRT and WCRT of any clock-domains are invariant of
% \emph{d} as explained in Section \ref{sec:intr-real-time}. It is our
% fundamental assumption to find \emph{d} in our benchmark programs.
% =======
% \begin{table}[t]
% \centering
%\twocolumn[
%\begin{@twocolumnfalse}
%\caption{Benchmark programs using \texttt{delay} constructs} \label{table:benchmark}
%\scalebox{0.85}{
%\begin{tabular}{|c| c | c | c | c | c | c | c |}
%	\cline{4-8}
% 	\multicolumn{3}{c|}{}											& HRTCS 		& Motor 		  & Robot 			  & AECS/CD1  		   & AECS/CD2\\ \hline
% 	\multirow{12}{*}{JOP} 		& \multicolumn{2}{|c|}{BCRT} 		&0.0334 ms 		& 0.0361 ms		  & 0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cline{2-8}   
% 								& \multicolumn{2}{|c|}{WCRT} 		&0.1120 ms 		& 0.1116 ms		  & 0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cline{2-8} 
% 								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cline{3-8} 
% 								&			   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
% 								&			   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 21 			  &	N/A				  & N/A      		   &N/A\\ \hline
% 	\multirow{12}{*}{TP-JOP} 	& \multicolumn{2}{|c|}{BCRT} 		&0.0028 ms 		& 0.0060 ms		  & 0.0011 ms		  & 0.0532 ms		   & 0.0292 ms\\ \cline{2-8}   
% 								& \multicolumn{2}{|c|}{WCRT} 		&0.0329 ms 		& 0.0393 ms		  & 0.0361 ms		  & 0.5072 ms		   & 0.8388 ms\\ \cline{2-8} 
% 								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-600.3 ms 	& 2.4-15.6265 ms  & 1230-42317.8276 ms& 10000-95358.8578 ms& 10000-287757.9834 ms \\ \cline{3-8} 
% 								&			   & d			 		&18209-18232 	& 398 			  & 1171429			  & 188015		       &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-10.8757 ms& N/A				  & N/A 			   &10000-287757.9834 ms\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 277			  & N/A				  & N/A       		   &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.3534 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 9		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.9631 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
% 								&			   & d				 	& 	N/A	 		& 50			  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-4.79 ms   & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
% 								&			   & d			 		& 	N/A	 		& 122 			  &	N/A				  & N/A      		   &N/A\\ \cline{2-8}
% 	\hline
% \end{tabular}
% }
% \end{@twocolumnfalse}
% ]
% \end{table}

\begin{figure}
\centering
	\includegraphics[trim=2cm 2cm 2cm 2cm,scale=0.5]{table2}
        \caption{Evaluation of logical delays \emph{d} for on various
          benchmark programs}\label{fig:comparison}
\end{figure}
%
We have carried out a number of experiments on a set of applications
with real-time constraints. The benchmark set is shown in
Figure~\ref{fig:comparison}. HRCTS is the human response system
described in Figure~\ref{fig:1}. AECS (Access and Environmental Control
System) is an application that controls an intelligent room environment
described in~\cite{aecs_ispa}. Motor is a stepper motor controller
from~\cite{Bourke2009a}. Robot is an industrial automation application
that consists of two manufacturing belts and a robotic arm that splits
goods according to their volumes. HRCTS consists of 2 CDs, but only one
with real-time delays. AECS also has 2 CDs; CD1 consist of a single
delay statement, while CD2 has 2 delay statements. Robot and Motor both
are synchronous programs with 1 and 5 delay statements,
respectively. All these examples are written in the SystemJ
language. Finally, except for HRCTS all other examples have exact (and
deterministic) delay requirements. These delay requirements are shown in
Figure~\ref{fig:comparison} (\texttt{M..N}).

@@

As one can see in Figure \ref{fig:comparison}, BCRT and WCRT were
calculated for all examples. Given the real-time \mbox{\texttt{delay
    (M..N)}} provided by programmers, required logical delay \texttt{d}
was determined by applying Algorithm~\ref{alg:1}. In HRTCS, real-time
delay of the range 50.3..200.3 (ms) is only satisfied when \emph{d} is
between 1506 and 1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}).  It is
then compiler's job to statically choose one of the values between this
range.

>>>>

% As one can see in Table \ref{table:benchmark}, BCRT and WCRT of overall
% programs are smaller when they run on TP-JOP. For example, WCRT and BCRT
% of HRTCS are \(\times\)11.9 and \(\times\)3.4 smaller, respectively, for
% TP-JOP (0.0028, 0.0329 ms) compared to JOP (0.0334, 0.1120 ms). On the
% other hand, required logical delays \emph{d} are generally bigger on
% TP-JOP e.g. \(\times\)4.5 - \(\times\)5.9 and \(\times\)30.9 in Motor
% and Robot respectively. It is expected as their BCRT and WCRT
% differences are bigger on TP-JOP.  This also led to greater increase in
% minimum upper real-time bounds \emph{N} for TP-JOP in every example.  In
% AECS, there are two clock-domains using delay constructs that each has
% their own BCRT and WCRT. Again, individual BCRT and WCRT is smaller
% whereas \emph{d} is bigger on TP-JOP. One important property to note
% here, is that BCRT and WCRT of any clock-domains are invariant of
% \emph{d} as explained in Section \ref{sec:intr-real-time}. It is our
% fundamental assumption to find \emph{d} in our benchmark programs.
% =======

\begin{table}[t]
 \centering
  \twocolumn[
\begin{@twocolumnfalse}
\caption{Benchmark programs using \texttt{delay} constructs} \label{fig:comparison}
\scalebox{0.85}{
\begin{tabular}{| c | c | c | c | c | c | c |}
	\cline{3-7}
	\multicolumn{2}{c|}{}											& HRTCS 		& Motor 		  & Robot 			  & AECS/CD1  		   & AECS/CD2\\ \hline
								 \multicolumn{2}{|c|}{BCRT} 		&0.0334 ms 		& 0.0361 ms		  & 0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cline{1-7}
								 \multicolumn{2}{|c|}{WCRT} 		&0.1120 ms 		& 0.1116 ms		  & 0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cline{1-7}
								 \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cline{2-7}
											   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cline{1-7}
								 \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cline{1-7}
								 \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cline{1-7}
								 \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cline{2-7}
											   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cline{1-7}
								 \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 21 			  &	N/A				  & N/A      		   &N/A\\ \hline
% 	\multirow{12}{*}{TP-JOP} 	& \multicolumn{2}{|c|}{BCRT} 		&0.0028 ms 		& 0.0060 ms		  & 0.0011 ms		  & 0.0532 ms		   & 0.0292 ms\\ \cline{2-8}
% 								& \multicolumn{2}{|c|}{WCRT} 		&0.0329 ms 		& 0.0393 ms		  & 0.0361 ms		  & 0.5072 ms		   & 0.8388 ms\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-600.3 ms 	& 2.4-15.6265 ms  & 1230-42317.8276 ms& 10000-95358.8578 ms& 10000-287757.9834 ms \\ \cline{3-8}
% 								&			   & d			 		&18209-18232 	& 398 			  & 1171429			  & 188015		       &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-10.8757 ms& N/A				  & N/A 			   &10000-287757.9834 ms\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 277			  & N/A				  & N/A       		   &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.3534 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 9		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.9631 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8}
% 								&			   & d				 	& 	N/A	 		& 50			  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-4.79 ms   & N/A				  &	N/A      		   &N/A\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 122 			  &	N/A				  & N/A      		   &N/A\\ \cline{2-8}
% 	\hline
		\end{tabular}
		}
  \end{@twocolumnfalse}
  ]
\end{table}

% \begin{figure}
% \centering
% 	\includegraphics[trim=2cm 2cm 2cm 2cm,scale=0.5]{table2}
%         \caption{Evaluation of logical delays \emph{d} for on various
%           benchmark programs}\label{fig:comparison}
% \end{figure}

We have carried out a number of experiments on a set of applications
with real-time constraints. The benchmark set is shown in
Table~\ref{fig:comparison}. HRCTS is the human response system
described in Figure~\ref{fig:1}. AECS (Access and Environmental Control
System) is an application that controls an intelligent room environment
described in~\cite{aecs_ispa}. Motor is a stepper motor controller
from~\cite{Bourke2009a}. Robot is an industrial automation application
that consists of two manufacturing belts and a robotic arm that splits
goods according to their volumes. HRCTS consists of 2 CDs, but only one
with real-time delays. AECS also has 2 CDs; CD1 consist of a single
delay statement, while CD2 has 2 delay statements. Robot and Motor both
are synchronous programs with 1 and 5 delay statements,
respectively. All these examples are written in the SystemJ
language. Finally, except for HRCTS all other examples have exact (and
deterministic) delay requirements. These delay requirements are shown in
Table~\ref{fig:comparison} (\texttt{M..N}).

@@

As one can see in Table \ref{fig:comparison}, BCRT and WCRT were
calculated for all examples. Given the real-time \mbox{\texttt{delay
    (M..N)}} provided by programmers, required logical delay \texttt{d}
was determined by applying Algorithm~\ref{alg:1}. In HRTCS, real-time
delay of the range 50.3..200.3 (ms) is only satisfied when \emph{d} is
between 1506 and 1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}).  It is
then compiler's job to statically choose one of the values between this
range.
